A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-11-13 kobakian-cook.Rmd
capitalisation of Figure

<!-- choropleth -->
The familiar choropleth map display is often used to allow the user to orient themselves. However, the emphasis on the land mass diminishes the features of the distribution in densely populated communities due to the small size on the display [@ACTUC]. The unique shapes of boundaries can be helpful for orienting users but may not contribute to their understanding of the spatial disease distribution as many of the communities are not visible in a choropleth display [@TVSSS]. Each Statistical Area at Level 2 (SA2) [@abs2011] was designed to represent a community. These administrative areas are often used to aggregate census data and used to understand demographics within communities of the Australian population. This presents an opportunity for explicit map transformations to improve communication of distributions [@CBATCC]. In figure \ref{fig:tas_displays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.

@@

When communicating information that is relevant to the population, each member of the population can be given equal representation by transforming the map [@TVSSS]. The impact of a disease over connected communities can be seen by allowing the boundaries to maintain connection in the transformed display. The contiguous cartogram displayed in figure \ref{fig:tas_displays}a) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP]. These new shapes can now be coloured to represent a second variable. The algorithm uses the geographic shape of the areas and iterates toward sizing the areas to represent the population. This display can create twisted and unfamiliar shapes from the geographic units as the algorithms must satisfy the topology conditions, especially when there are communities located geographically far from their neighbours [@TVSSS].

@@

The non-contiguous cartogram in figure \ref{fig:tas_displays}b) also uses the population to rescale the geographic units. Unlike the contiguous cartogram, the SA2 areas maintain their geographic shape, but they may not retain the connection with their neighbours. The population of the SA2 areas is used to scale the geographic units in the non-contiguous cartogram [@NAC]. The amount of white space can be meaningful in non-contiguous cartograms [@ECGC], in this example the disparity between large rural areas and small urban areas means that the city of Hobart may look reasonable but these units are not visible in the context of the Tasmania state map. Depending on the difference between the population and geographic land size, the amount of white space can also prevent meaningful understanding of the distribution [@TVSSS].

@@

The Dorling cartogram presents each geographic unit as a circle, the size of the circle is scaled according to the population value of each area [@ACTUC]. Figure \ref{fig:tas_displays}c) shows the Tasmania SA2 areas as an individual circle located as close as possible to the geographic centroid location. This map draws attention to the collection of coastal cities in Tasmania that were not apparent in figure \ref{fig:tas_displays} a), or b). This display also highlights that the approximation of equal population is not easy to fulfil, as there is some disparity in the sizes of the circles.

>>>>

<!-- choropleth -->
The familiar choropleth map display is often used to allow the user to orient themselves. However, the emphasis on the land mass diminishes the features of the distribution in densely populated communities due to the small size on the display [@ACTUC]. The unique shapes of boundaries can be helpful for orienting users but may not contribute to their understanding of the spatial disease distribution as many of the communities are not visible in a choropleth display [@TVSSS]. Each Statistical Area at Level 2 (SA2) [@abs2011] was designed to represent a community. These administrative areas are often used to aggregate census data and used to understand demographics within communities of the Australian population. This presents an opportunity for explicit map transformations to improve communication of distributions [@CBATCC]. In Figure \ref{fig:tas_displays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.

@@

When communicating information that is relevant to the population, each member of the population can be given equal representation by transforming the map [@TVSSS]. The impact of a disease over connected communities can be seen by allowing the boundaries to maintain connection in the transformed display. The contiguous cartogram displayed in Figure \ref{fig:tas_displays}a) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP]. These new shapes can now be coloured to represent a second variable. The algorithm uses the geographic shape of the areas and iterates toward sizing the areas to represent the population. This display can create twisted and unfamiliar shapes from the geographic units as the algorithms must satisfy the topology conditions, especially when there are communities located geographically far from their neighbours [@TVSSS].

@@

The non-contiguous cartogram in Figure \ref{fig:tas_displays}b) also uses the population to rescale the geographic units. Unlike the contiguous cartogram, the SA2 areas maintain their geographic shape, but they may not retain the connection with their neighbours. The population of the SA2 areas is used to scale the geographic units in the non-contiguous cartogram [@NAC]. The amount of white space can be meaningful in non-contiguous cartograms [@ECGC], in this example the disparity between large rural areas and small urban areas means that the city of Hobart may look reasonable but these units are not visible in the context of the Tasmania state map. Depending on the difference between the population and geographic land size, the amount of white space can also prevent meaningful understanding of the distribution [@TVSSS].

@@

The Dorling cartogram presents each geographic unit as a circle, the size of the circle is scaled according to the population value of each area [@ACTUC]. Figure \ref{fig:tas_displays}c) shows the Tasmania SA2 areas as an individual circle located as close as possible to the geographic centroid location. This map draws attention to the collection of coastal cities in Tasmania that were not apparent in Figure \ref{fig:tas_displays} a), or b). This display also highlights that the approximation of equal population is not easy to fulfil, as there is some disparity in the sizes of the circles.

### 2020-11-13 kobakian-cook.tex
capitalisation of Figure

The familiar choropleth map display is often used to allow the user to
orient themselves. However, the emphasis on the land mass diminishes the
features of the distribution in densely populated communities due to the
small size on the display \citep{ACTUC}. The unique shapes of boundaries
can be helpful for orienting users but may not contribute to their
understanding of the spatial disease distribution as many of the
communities are not visible in a choropleth display \citep{TVSSS}. Each
Statistical Area at Level 2 (SA2) \citep{abs2011} was designed to
represent a community. These administrative areas are often used to
aggregate census data and used to understand demographics within
communities of the Australian population. This presents an opportunity
for explicit map transformations to improve communication of
distributions \citep{CBATCC}. In figure \ref{fig:tas_displays} the
choropleth map can be seen underneath each alternative map display to
allow for comparisons to be made.

@@

When communicating information that is relevant to the population, each
member of the population can be given equal representation by
transforming the map \citep{TVSSS}. The impact of a disease over
connected communities can be seen by allowing the boundaries to maintain
connection in the transformed display. The contiguous cartogram
displayed in figure \ref{fig:tas_displays}a) draws attention to smaller
geographic units when they are rescaled according to the population
\citep{DMAHP}. These new shapes can now be coloured to represent a
second variable. The algorithm uses the geographic shape of the areas
and iterates toward sizing the areas to represent the population. This
display can create twisted and unfamiliar shapes from the geographic
units as the algorithms must satisfy the topology conditions, especially
when there are communities located geographically far from their
neighbours \citep{TVSSS}.

The non-contiguous cartogram in figure \ref{fig:tas_displays}b) also
uses the population to rescale the geographic units. Unlike the
contiguous cartogram, the SA2 areas maintain their geographic shape, but
they may not retain the connection with their neighbours. The population
of the SA2 areas is used to scale the geographic units in the
non-contiguous cartogram \citep{NAC}. The amount of white space can be
meaningful in non-contiguous cartograms \citep{ECGC}, in this example
the disparity between large rural areas and small urban areas means that
the city of Hobart may look reasonable but these units are not visible
in the context of the Tasmania state map. Depending on the difference
between the population and geographic land size, the amount of white
space can also prevent meaningful understanding of the distribution
\citep{TVSSS}.

The Dorling cartogram presents each geographic unit as a circle, the
size of the circle is scaled according to the population value of each
area \citep{ACTUC}. Figure \ref{fig:tas_displays}c) shows the Tasmania
SA2 areas as an individual circle located as close as possible to the
geographic centroid location. This map draws attention to the collection
of coastal cities in Tasmania that were not apparent in figure
\ref{fig:tas_displays} a), or b). This display also highlights that the
approximation of equal population is not easy to fulfil, as there is
some disparity in the sizes of the circles.

>>>>

The familiar choropleth map display is often used to allow the user to
orient themselves. However, the emphasis on the land mass diminishes the
features of the distribution in densely populated communities due to the
small size on the display \citep{ACTUC}. The unique shapes of boundaries
can be helpful for orienting users but may not contribute to their
understanding of the spatial disease distribution as many of the
communities are not visible in a choropleth display \citep{TVSSS}. Each
Statistical Area at Level 2 (SA2) \citep{abs2011} was designed to
represent a community. These administrative areas are often used to
aggregate census data and used to understand demographics within
communities of the Australian population. This presents an opportunity
for explicit map transformations to improve communication of
distributions \citep{CBATCC}. In Figure \ref{fig:tas_displays} the
choropleth map can be seen underneath each alternative map display to
allow for comparisons to be made.

@@

When communicating information that is relevant to the population, each
member of the population can be given equal representation by
transforming the map \citep{TVSSS}. The impact of a disease over
connected communities can be seen by allowing the boundaries to maintain
connection in the transformed display. The contiguous cartogram
displayed in Figure \ref{fig:tas_displays}a) draws attention to smaller
geographic units when they are rescaled according to the population
\citep{DMAHP}. These new shapes can now be coloured to represent a
second variable. The algorithm uses the geographic shape of the areas
and iterates toward sizing the areas to represent the population. This
display can create twisted and unfamiliar shapes from the geographic
units as the algorithms must satisfy the topology conditions, especially
when there are communities located geographically far from their
neighbours \citep{TVSSS}.

The non-contiguous cartogram in Figure \ref{fig:tas_displays}b) also
uses the population to rescale the geographic units. Unlike the
contiguous cartogram, the SA2 areas maintain their geographic shape, but
they may not retain the connection with their neighbours. The population
of the SA2 areas is used to scale the geographic units in the
non-contiguous cartogram \citep{NAC}. The amount of white space can be
meaningful in non-contiguous cartograms \citep{ECGC}, in this example
the disparity between large rural areas and small urban areas means that
the city of Hobart may look reasonable but these units are not visible
in the context of the Tasmania state map. Depending on the difference
between the population and geographic land size, the amount of white
space can also prevent meaningful understanding of the distribution
\citep{TVSSS}.

The Dorling cartogram presents each geographic unit as a circle, the
size of the circle is scaled according to the population value of each
area \citep{ACTUC}. Figure \ref{fig:tas_displays}c) shows the Tasmania
SA2 areas as an individual circle located as close as possible to the
geographic centroid location. This map draws attention to the collection
of coastal cities in Tasmania that were not apparent in Figure
\ref{fig:tas_displays} a), or b). This display also highlights that the
approximation of equal population is not easy to fulfil, as there is
some disparity in the sizes of the circles.
